Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/supplement.tex
added missing figures
fixed the supplement

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning.pdf}
\caption{
    \textbf{Normalized mean enclosing block length}, $\bar l_B(m,x)$, after $T=1000$ generations,
    against position relative to the selected locus (horizontal axis)
    located in the center of a 1M chromosome.
    Each line shows the mean block length at that spatial and genomic position
    divided by the mean over the chromosome at that location;
    the simulation was run with $s=1$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals.
}\label{Fig:blockLengths}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmapAncBConditioning.pdf}
\caption{Heatmap of mean block length $l_B(m)$ along a simulated chromosome under $T=1000$, $s=1$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals. }\label{Supp:blockLengthHeatmap}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromNoConditioning.pdf}
\caption{Mean block length $l(m)$ surrounding a given position along the genome with a single underdominant site ($s=0.01, T=1000$). }\label{Supp:blockLengthNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmap.pdf}
\caption{Heatmap of mean block length $l(m)$ along a simulated chromosome with a single underdominant site ($s=0.01, T=1000$) }\label{Supp:blockLengthHeatmapNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/adjacentBlocksAlongChromAncBConditioning.pdf}
\caption{Mean block length of $l_A(m\pm)$ across chromosome with single under dominant site, conditioning on ancestry $B$ at the selected locus. ($s=0.01, T=1000$)}\label{Supp:adjacentBlocks}
\end{figure}

\begin{figure}
\includegraphics{figs/s0point01_ratioAdjacentBlocksAlongChromAncBConditioningHighRes.pdf}
    \caption{The statistic $\bar C(m,x)$: the ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and mean adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme. This  simulation corresponds to that represented in Figure~\ref{Fig:blockLengthsZoom}; note the difference in y-axis scale.}\label{Supp:ratioBlockAdjacent}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromHeatmapAncBConditioning.pdf}
    \caption{Heatmap of $C(m,x)=\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$). }\label{Supp:ratioBlockAdjacentHeatmap}
\end{figure}

@@

\begin{figure}
    \includegraphics{figs/s001_adjacentBlocksAlongChromAncBConditioning}
    \includegraphics{figs/s001_adjacentBlocksAlongChromNoConditioningHighRes}
        \caption{
     Block lengths along chromosome under $s=0.001$, conditioning on ancestry B (top) and without conditioning (bottom) } \label{sfig:blockLengthPlot_t1000_s0.001}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning.pdf}
\caption{
    \textbf{Normalized mean enclosing block length}, $\bar l_B(m,x)$, after $T=1000$ generations,
    against position relative to the selected locus (horizontal axis)
    located in the center of a 1M chromosome.
    Each line shows the mean block length at that spatial and genomic position
    divided by the mean over the chromosome at that location;
    the simulation was run with $s=0.01$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals.
}\label{Fig:blockLengths}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmapAncBConditioning.pdf}
\caption{Heatmap of mean block length $l_B(m)$ along a simulated chromosome under $T=1000$, $s=0.01$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals. }\label{Supp:blockLengthHeatmap}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromNoConditioning.pdf}
\caption{Mean block length $l(m)$, without conditioning on ancestry, surrounding a given position along the genome with a single underdominant site with parameters as for Fig~\ref{Fig:blockLengths}. ($s=0.01, T=1000, \sigma=1$). }\label{Supp:blockLengthNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmap.pdf}
\caption{Heatmap of mean block length $l(m)$, without conditioning on ancestry, along a simulated chromosome with a single underdominant site, with parameters as for Fig~\ref{Fig:blockLengths} ($s=0.01, T=1000, \sigma=1$) }\label{Supp:blockLengthHeatmapNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/adjacentBlocksAlongChromAncBConditioning.pdf}
\caption{Mean block length of $l_A(m\pm)$ across chromosome with single under dominant site, conditioning on ancestry $B$ at the selected locus, with parameters as for Fig~\ref{Fig:blockLengths} ($s=0.01, T=1000, \sigma=1$)}\label{Supp:adjacentBlocks}
\end{figure}

\begin{figure}
\includegraphics{figs/s0point01_ratioAdjacentBlocksAlongChromAncBConditioningHighRes.pdf}
    \caption{The normalized statistic $\bar C(m,x)$: the ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and mean adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme. This  simulation corresponds to that represented in Figure~\ref{Fig:blockLengthsZoom}; note the difference in y-axis scale.}\label{Supp:ratioBlockAdjacent}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromHeatmapAncBConditioning.pdf}
    \caption{Heatmap of $C(m,x)=\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site and parameters as for Fig.~\ref{Fig:blockLengths} ($s=0.01, T=1000, \sigma=1$). }\label{Supp:ratioBlockAdjacentHeatmap}
\end{figure}

@@

\begin{figure}
    \includegraphics{figs/s001_adjacentBlocksAlongChromAncBConditioning}
    \includegraphics{figs/s001_adjacentBlocksAlongChromNoConditioningHighRes}
        \caption{
     Block lengths along chromosome under $s=0.001$ and other parameters as for Fig.~\ref{Fig:blockLengths}, conditioning on ancestry B (top) and without conditioning (bottom) } \label{sfig:blockLengthPlot_t1000_s0.001}
\end{figure}
